\cvsection{Projects}
\begin{cventries}
    \cventry 
    {Active Contributor}
    {Debian Project}
    {Remote work}
    {March 2016 - present}
    {\begin{cvitems}
        \item {PEAR Packager for PHP Debian group, and Junior developer for Debian Octave Group.}
        \item {Packaged two dependency libraries for GNU-Social project in FreedomBox, a personalized and private home server.}
        \item {An online consultant to the Debian new users forum.}
    \end{cvitems}}
    \cventry
    {Linux Consultant and Helper Student BE Projects}
    {JNTUH}
    {Telangana, Hyderabad, India}
    {January 2014 - December 2016}
    {
        \begin{cvitems}
        \item {Speaker, Supporter, and Mentor for Linux training sessions in GLUG. Configured automatic controlling of paper presentations in collage annual fests using RaspberryPi open hardware.}
        \item Configured a Linux based VoIP server for testing use cases of FreedomBox project, a personalized home server.
        \item {Worked on OpenWRT and BeagleBoneBlack hardware to create an Access Point instance, and College Radio instance using GNU Radio.}
        \item {Mentored/Volunteered projects: Open Hardware solution for small business applications, Open Source VoIP usnig Yate, Decryption of Cryptography Ciphers of Indian Languages, and Government School Teachers Training sessions on Linux usage,}
        \end{cvitems}
    }
    \cventry
    {Team Lead}
    {BE, ME Course Projects}
    {}
    {}
    {
        \begin{cvitems}
            \item {BE final project is on  License Plate Detection and Text Extraction using BeagleBoneBlack by utilizing K-NN algorithm, and later presented to the Government Traffic Police Authority as a POC - November 2017.}
            \item {Machine Vision course project is on Thai License Plate Detection using SVM and Sliding window approach - April 2017.}
            \item {Decision Support Technologies course project is on Daily-Base Food Recommendation System as a website - April 2017.}
            \item {E-Business course project is on Social Dating website - November 2017.}
        \end{cvitems}
    }
    \cventry
    {Active Contributor}
    {Mozilla Project}
    {}
    {March 2014 - present}
    {
        \begin{cvitems}
        \item {Co-organized 1-day workshop on Firefox OS- Apps, Active campaigner for Mozilla project, Active contributor for L10n Telugu localization project, Organized Firefox Quantum Testing Day, and tested different sites for Quantum release.}
        \end{cvitems}
    }
    \cventry
    {Web Developer}
    {Drupal Based Projects}
    {}{March 2015 - present}
    {
        \begin{cvitems}
        \item {Developed a Drupal based websites for the college annual fests, and a Social Dating site for an academic course project.}
        \end{cvitems}
    }
    %\cventry
    %{Request System Admin}
    %{Open Access Button (OAB) Project}
    %{Remote work}
    %{July 2017 - present}
    %{
    %    \begin{cvitems}
    %        \item {Made different types of requests for research %articles from authors.}
    %    \end{cvitems}
    %}
    
\end{cventries}
\clearpage